Mahotas: Open source software for scriptable computer vision

### 2012-08-31 paper.tex
TXT Update timings after mahotas update

\begin{table}
\centering
\begin{tabular}{lrrrrr}
\toprule
Operation & mahotas & pymorph & scikits-image & OpenCV\\
\midrule
erode       &     12.2 &     14.4 &     41.9 &      0.4 & \\
dilate      &     13.4 &      9.0 &     39.4 &      0.4 & \\
open        &     25.6 &     23.4 &     81.3 &       NA & \\
center mass &      7.1 &       NA &       NA &       NA & \\
sobel       &     81.9 &       NA &    106.5 &      6.2 & \\
cwatershed  &    194.8 &  56928.5 &    288.9 &     42.9 & \\
daubechies  &     20.7 &       NA &       NA &       NA & \\
haralick    &    326.9 &       NA &   7497.4 &       NA & \\
\bottomrule
\end{tabular}
\caption{Efficiency Results for mahotas, pymorph, scikits-image, and openCV
(through Python wrappers). Shown are values as multiples of the time that
\code{numpy.max(f)} takes.}
\label{tab:efficiency}
\end{table}

@@

OpenCV is the fastest library, but this comes at the cost of some flexibility.
Arguments to its functions must be of the exact expected type and it is
possible to crash the interpreter if types do match the expected type (in the
other libraries, all types are checked and an exception is generated which can
be caught by user code). This is particularly relevant for interactive use.

>>>>

\begin{table}
\centering
\begin{tabular}{lrrrrr}
\toprule
Operation & mahotas & pymorph & scikits-image & OpenCV\\
\midrule
erode       &     10.3 &     14.2 &     41.5 &      0.4 & \\
dilate      &     12.7 &      8.9 &     38.9 &      0.4 & \\
open        &     23.0 &     23.3 &     80.8 &       NA & \\
center mass &      7.1 &       NA &       NA &       NA & \\
sobel       &     75.4 &       NA &    105.4 &      6.2 & \\
cwatershed  &    191.3 &  60410.0 &    285.0 &     42.1 & \\
daubechies  &     20.3 &       NA &       NA &       NA & \\
haralick    &    304.5 &       NA &   7615.8 &       NA & \\
\bottomrule
\end{tabular}
\caption{Efficiency Results for mahotas, pymorph, scikits-image, and openCV
(through Python wrappers). Shown are values as multiples of the time that
\code{numpy.max(image)} takes to compute the maximum pixel value in the image
(all operations are over the same image). For scikits-image, features on the
grey-scale cooccurrence matrix were used instead of Haralick features, which it
does not support.}
\label{tab:efficiency}
\end{table}

@@

OpenCV is the fastest library, but this comes at the cost of some flexibility.
Arguments to its functions must be of the exact expected type and it is
possible to crash the interpreter if types do match the expected type (in the
other libraries, all types are checked and an exception is generated which can
be caught by user code). This is particularly relevant for interactive use as
the user is often exploring and is willing to pay the cost of a few extra type
conversions to avoid a hard-crash.
